---
title: "Kaggle competition_House Prices"
author: "Roy Wang"
date: "7/17/2017"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE)
```
## Introduction

Hello everyone! I'm a machine learning novice, and this is my first kernal writup. 

My random number is `r rnorm(10)`.

```{r, echo=TRUE}
set.seed(490)
NewList <- sample(3:28, 5, replace = TRUE)
```

My sample is `r NewList`.

```{r, echo=TRUE, results="hide"}
x <- rnorm(10)
y <- x + rnorm(10, sd = 3)
plot(x, y, main = "My rnorm scatterplot")
```

Below is a table of linear regression:

```{r, echo=TRUE}
data("mtcars")
linear.model <- lm(wt ~ ., data = mtcars)
plot(linear.model)
summary(linear.model)
```

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars, echo=FALSE}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
